\section{Description of the Sifteo Cubes}

\textbf{Taken from the Sifteo FAQ}


\subsection{How do Sifteo Cubes work?}
Sifteo Cubes is a hands-on interactive game system. They communicate wirelessly to respond to each other and being tilted, shaken, flipped, and pressed. The Sifteo Base stores your games and plays audio. You can play with 3-12 Sifteo cubes at once!\\
Sifteo Cubes use 1 AAA battery each. Sifteo Bases use 2 AAA batteries. Rechargeable nickel metal hydride (NiMH) batteries, standard alkaline, or lithium (non-rechargeable) batteries will each work. Batteries last for approximately 8 hours of gameplay.

\subsection{Who are Sifteo Cubes for?}
Sifteo Cubes are perfect for kids and kids at heart who geek out on brainy challenging games and cool new gadgets (recommended for ages 7 to adult). Our games can be played individually and with friends and family. Sifteo Cubes are sturdy and can withstand some abuse. Still, they are sophisticated electronic devices, and very rough handling (throwing, dunking in water, and other forms of cube torture) can break a cube permanently.

\subsection{How do I play games on my cubes?}
Sifteo Cubes come pre-installed with 4 games that work right out of the box. You can buy more games using the Sifteo desktop software (download here) and install them by connecting the Sifteo Base to your computer with the USB cable that comes with it. Sifteo games are 80-120 credits (about $8-$12) each. You can buy credits through the desktop software.
View full tech specs and system requirements here .
